### 2022-05-13 mycv/subs/papers.tex
snapshot

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
  {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
  {}
  {in preparation}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
  {International Journal of Plasticity}
  {Vol. 135, 102812, 2020}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D. Steglich}
  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
  {International Journal of Mechanical Sciences}
  {Vol. 181, 105680, 2020}
  {
  }

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1088/1361-651X/ab4b66}{Extension of the VPSC model to account for elasto-visco-plastic behavior using a perturbed viscoplastic approach}}
  {Modelling and Simulation in Materials Science and Engineering}
  {Vol. 27(8) 085013, 2019}
  {
  }

@@

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, Timo Manninen}
  {\href{https://doi.org/10.1007/s12540-019-00292-5}{Enhancement in viscoplastic self-consistent FLD prediction model and its application for austenitic and ferritic stainless steels}}
  {Metals and Materials International}
  {Vol. 25(6) pp1548-1563, 2019}
  {
  }

@@

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, F. Barlat, C. N. Tom\'{e}, W. Wen}
  {\href{http://dx.doi.org/10.1016/j.ijplas.2016.07.015}{A comparative study between micro- and macro-mechanical constitutive models developed for complex loading scenarios}}
  {International Journal of Plasticity}
  {Vol. 93 p212-228, 2017} % etcs
  {
  }

@@

  \cventry
  {F. Barlat, \underline{Y. Jeong}, J. Ha, C. N. Tom\'{e}, M.-G. Lee, W. Wen}
  {\href{https://dx.doi.org/10.4028/www.scientific.net/KEM.725.3}{Advances in Constitutive Modeling of Plasticity for Forming Applications}}
  {Key Engineering Materials}
  {Vol. 725, p3-14, 2017}
  {
  }

  \cventry
  {\underline{Y. Jeong}, F. Barlat, C. N. Tom\'{e}, W. Wen}
  {\href{http://dx.doi.org/10.1063/1.4963544}{Validation of Homogeneous Anisotropic Hardening Approach Based on Crystal Plasticity}}
  {AIP Conference Proceedings}
  {Vol. 1769, 160001, 2016}
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {Extension of the VPSC model to account for elasto-visco-plastic behavior using a perturbed viscoplastic approach}
  {Modelling and Simulation in Materials Science and Engineering}
  {Vol. 27(8), 2019}
  {
  }

@@

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, Timo Manninen}
  {\href{10.1007/s12540-019-00292-5}{Enhancement in viscoplastic self-consistent FLD prediction model and its application for austenitic and ferritic stainless steels}}
  {Metals and Materials International}
  {Vol. 25(6), 2019}
  {
  }

@@

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, F. Barlat, C. Tom\'{e}, W. Wen}
  {\href{http://dx.doi.org/10.1016/j.ijplas.2016.07.015}{A comparative study between micro- and macro-mechanical constitutive models developed for complex loading scenarios}}
  {International Journal of Plasticity}
  {Vol. 93 p212-228, 2017} % etcs
  {
  }

@@

  \cventry
  {F. Barlat, \underline{Y. Jeong}, J. Ha, C Tom\'{e}, Myoung-Gyu Lee, W. Wen}
  {\href{https://dx.doi.org/10.4028/www.scientific.net/KEM.725.3}{Advances in Constitutive Modeling of Plasticity for Forming Applications}}
  {Key Engineering Materials}
  {Vol. 725, p3-14, 2017}
  {
  }

  \cventry
  {\underline{Y. Jeong}, F. Barlat, C. Tom\'{e}, W. Wen}
  {\href{http://dx.doi.org/10.1063/1.4963544}{Validation of Homogeneous Anisotropic Hardening Approach Based on Crystal Plasticity}}
  {AIP Conference Proceedings}
  {Vol. 1769, 160001, 2016}
  {
  }
